Program Transformations for miniKanren

### 2020-05-22 papers/miniKanren/text/nonconj.tex
propose a small extension for Unfolding subsection

The most important question is when to unfold.
Unfortunately, too much unfolding is sometimes is even worse than not enough unfolding.
There is a fine edge between those.
This problem is mentioned in the (CONTROL PAPER).
We believe that the following heuristic provides a reasonable control.

>>>>

The most important question is when to unfold.
\db{
  {\color{blue}PROPOSED EXTENSION:}, and when to stop unfolding even if the relation call seems to be good for specialization.
  Usually, unfolding in functional programming languages specialization, as well as inlining in imperative one, is considered to be safe from a residual program efficiency point of view.
  It may only lead to code explosion or code duplication which is mostly left to a target program compiler optimization or even is out of consideration at all if specializer is considered as a standalone tool~\cite{jonesbook}.
  Unfortunately, this is not the case for the specialization of relational programming language.
  Unlike functional and imperative, in relational programming language unfolding may easily affect the target program efficiency.
  It is crucial not to unfold too much since, for example, extra unifications or even repeated computations generated by optimized relation calls and further propagated to neighbouring conjunction may appear.
}
\db{{\color{blue}Unfortunately $\to$ }That is}, too much unfolding is sometimes is even worse than not enough unfolding.
There is a fine edge between those.
This problem is mentioned in the (CONTROL PAPER).
We believe that the following heuristic provides a reasonable control.
